```{r}
#importing needed library
library (matlib)
library(ggplot2)
library (rsample)
library(dplyr)
library(tidyr)
library (rsample)
library(glmnet)
library(visdat)
library(MASS)
```
```{r}
# Read customer shopping mall dataset from csv file
customer_shopping_data = as.matrix(read.csv(file="C:/Users/neupa/Downloads/customer_shopping_data_1695379411426 (1).csv",header = TRUE))
head(customer_shopping_data)
```
```{r}
# check missing values in data
missing_values <- is.na(customer_shopping_data)
missing_values_count <- colSums(missing_values)
missing_values_count
```
# There is no any missing values in customer_shopping mall dataset.

```{r}
# convert shopping data into dataframe
customer_shopping_data <- as.data.frame(customer_shopping_data)
head(customer_shopping_data)
```

```{r}
# summary statistics of each attributes
summary(customer_shopping_data)
```
# All attributes in dataset are in string type. so we have to change invoice_date into date format and categorical value into numerical values.
```{r}
# identify unique age group
unique_age <-unique(customer_shopping_data$age)
print(unique_age)
```
```{r}
# Generate counts for unique ages
age_counts <- table(customer_shopping_data$age)

# Create a data frame with unique ages and their counts
unique_age_with_counts <- data.frame(age = as.numeric(names(age_counts)), count = as.numeric(age_counts))
unique_age_with_counts <- unique_age_with_counts[order(unique_age_with_counts$count, decreasing = TRUE), ]

# View the unique ages with their counts
print(unique_age_with_counts)
```
# These are the top 10 age who made purchase in above shopping mall between 2021 and early 2023 AD.
```{r}
# identify unique gender present in data
unique_gender <-unique(customer_shopping_data$gender)
print(unique_gender)
```
```{r}
# unique catgory present in dataframe
unique_category <-unique(customer_shopping_data$category)
print(unique_category)
```
# In shopping mall , different eight category items are found.
```{r}
# unique payment method
unique_payment_method <- unique(customer_shopping_data$payment_method)
print(unique_payment_method)
```
# while purchase items, there are three ways to make payment either from cash or credit card or debit card.

```{r}
# shopping mall present in dataset
unique_shopping_mall <- unique(customer_shopping_data$shopping_mall)
unique_shopping_mall
```
```{r}
# define input variable
x <- customer_shopping_data[,!(names(customer_shopping_data) %in% c("invoice_no","customer_id","gender","shopping_mall"))]
x
```

```{r}
# convert invoice_date to Date format 
customer_shopping_data$invoice_date <- as.Date(customer_shopping_data$invoice_date,format = "%d/%m/%Y")

# extract from invoice_date to year
customer_shopping_data$invoice_year <- format(customer_shopping_data$invoice_date,"%Y")
# create a time series object with monthly frequency(assuming data is monthly)
customer_shopping_data.ts <-ts(x,start = c(as.numeric(format(min(customer_shopping_data$invoice_date),"%Y")),
                                  as.numeric(format(min(customer_shopping_data$invoice_date),"%m"))),
                    end = c(as.numeric(format(max(customer_shopping_data$invoice_date),"%Y")),as.numeric(format(max(customer_shopping_data$invoice_date),"%m"))),frequency = 12)

```
```{r}
head(customer_shopping_data)
```
```{r}
summary(customer_shopping_data)
```


```{r}

payment_df <- customer_shopping_data %>%
  group_by(invoice_year,payment_method) %>%
  summarize(payment_value = n())

# Print the resulting dataframe
print(payment_df)
```
# From this table, we can say that in every most of the customer made cash payment rather than credit or debit card.
```{r}
category_df <- customer_shopping_data %>%
  group_by(invoice_year,category) %>%
  summarize(category_value = n())
# Pivot the dataframe to get category as columns
cateory_pivot_df <- category_df %>%pivot_wider(names_from = category, values_from = category_value)
# Reshape the data for plotting
plot_data <- cateory_pivot_df %>%
  gather(key = "category", value = "category_value", -invoice_year)

# Plot
ggplot(plot_data, aes(x = invoice_year, y = `category_value`, color = `category`, group = `category`)) +
  geom_line() +
  labs(title = "category Comparison Over Years",
       x = "Year", y = "category value",
       color = "category") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 1)) +
  scale_color_manual(values = c("Books" = "blue", "Clothing" = "red", "Cosmetics" = "green","Food & Beverage
" = "purple", "Shoes" = "orange", "Souvenir" = "yellow","Technology"="light blue","Toys"="light green"))

```
# This line chart shows that the most sold category is clothing and least in books.


```{r}
# Pivot the dataframe to get payment methods as columns
pivot_df <- payment_df %>%
  pivot_wider(names_from = payment_method, values_from = payment_value)
# Reshape the data for plotting
plot_data <- pivot_df %>%
  gather(key = "Payment Method", value = "Payment Count", -invoice_year)

# Plot
ggplot(plot_data, aes(x = invoice_year, y = `Payment Count`, color = `Payment Method`, group = `Payment Method`)) +
  geom_line() +
  labs(title = "Payment Methods Comparison Over Years",
       x = "Year", y = "Payment Count",
       color = "Payment Method") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 1)) +
  scale_color_manual(values = c("Cash" = "blue", "Credit Card" = "red", "Debit Card" = "green"))
```

```{r}
# Define the function to categorize age
categorize_age <- function(age) {
  case_when(
    age < 20 ~ 'teenage',
    age >= 20 & age <= 35 ~ 'adults',
    age > 35 & age <= 50 ~ 'late middle age',
    TRUE ~ 'old'
  )
}

# Apply the function to create a new column indicating the age group
customer_shopping_data$age_group <- categorize_age(customer_shopping_data$age)

# Print the resulting dataframe
print(customer_shopping_data)


```
```{r}
age_group_df <- customer_shopping_data %>%
  group_by(invoice_year,age_group) %>%
  summarize(age_group_value = n())

# Print the resulting dataframe
print(age_group_df)
```
# we categorize age into different groups such as below 20,teenage;>=20 and <=35,adults;>35 and <=50, late middle age and above them old.In 2021 and 2022, old age people made more shopping and In 2023, adults do .
```{r}
# Pivot the dataframe to get payment methods as columns
age_pivot_df <- age_group_df %>%
  pivot_wider(names_from = age_group, values_from = age_group_value)

# Reshape the data for plotting
plot_data <- age_pivot_df %>%
  gather(key = "age_group", value = "age_group_value", -invoice_year)

# Plot
ggplot(plot_data, aes(x = invoice_year, y = `age_group_value`, color = `age_group`, group = `age_group`)) +
  geom_line() +
  labs(title = "age categorize Comparison Over Years",
       x = "Year", y = "age_group_value",
       color = "age_group") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 1)) +
  scale_color_manual(values = c("teenage" = "blue", "adults" = "red", "late middle age" = "green","old" = "purple"))
```
```{r}
# convert gender to numerical values
customer_shopping_data$gender <- as.numeric(factor(customer_shopping_data$gender,levels = unique(customer_shopping_data$gender)))


# convert category to numerical values
customer_shopping_data$category <- as.numeric(factor(customer_shopping_data$category,levels = unique(customer_shopping_data$category)))

# convert payment method to numerical values
customer_shopping_data$payment_method <- as.numeric(factor(customer_shopping_data$payment_method,levels = unique(customer_shopping_data$payment_method)))

# convert shopping mall to numerical values
customer_shopping_data$shopping_mall <- as.numeric(factor(customer_shopping_data$shopping_mall,levels = unique(customer_shopping_data$shopping_mall)))

tail(customer_shopping_data)
```

```{r}
# define input variable
x <- customer_shopping_data[,!(names(customer_shopping_data) %in% c("invoice_no","customer_id","gender","shopping_mall"))]
x
```
```{r}
# task 1.1
customer_shopping_data$invoice_date <- as.Date(customer_shopping_data$invoice_date,format = "%d/%m/%Y")

customer_shopping_data$quantity <- as.numeric(customer_shopping_data$quantity)

# extract year and month from invoice date
customer_shopping_data$year_month <- format(customer_shopping_data$invoice_date,"%Y-%m")


# Aggregate quantity by year-month
aggregated_data <- aggregate(quantity ~ year_month, data = customer_shopping_data, sum)


# convert year_month to date format for plotting
aggregated_data$year_month <- as.Date(paste0(aggregated_data$year_month, "-01"))


#create a time series object with monthly frequency
customer_shopping_data.ts <- ts(aggregated_data$quantity, start = c(as.numeric(format(min(aggregated_data$year_month),"%Y")),
                                                           as.numeric(format(min(aggregated_data$year_month),"%m"))),
                       end = c(as.numeric(format(max(aggregated_data$year_month),"%Y")),
                               as.numeric(format(max(aggregated_data$year_month),"%m"))),frequency = 12)
plot(customer_shopping_data.ts,main = "Time series plot of Output(grouped by year-month)",xlab = "year-month",ylab = "Total quantity")

```
```{r}
## Task 1.2
x$price <- as.numeric(x$price)
density_of_price = density(x$price)
plot(density_of_price,main = "Density plot of price")
```

```{r}
# creating  a Histogram of X inputs
hist(x$price,freq = FALSE,main = "Histogram and density plot of price",xlab = "Price")
lines(density_of_price, lwd = 2, col = "black")
rug(jitter(x$price))
```
```{r}
# Convert payment method to numerical values with labels
customer_shopping_data$payment_method <- as.numeric(factor(customer_shopping_data$payment_method, levels = unique(customer_shopping_data$payment_method)))
# Display numerical values and their corresponding labels
method_labels <- levels(factor(customer_shopping_data$payment_method))
method_values <- unique(unique_payment_method)
unique_payment_method_mapping <- data.frame(Numerical_Value = method_labels, payment_method = method_values)
print(unique_payment_method_mapping)
```
```{r}
# density of payment_method
density_of_payment = density(x$payment)
plot(density_of_payment,main = "Density plot of payment")
# creating  a Histogram of X inputs
hist(x$payment,freq = FALSE,main = "Histogram and density plot of payment",xlab = "payment_method")
lines(density_of_payment, lwd = 2, col = "black")
rug(jitter(x$payment_method))
```
```{r}
x$age <- as.numeric(x$age)
# density of payment_method
density_of_age = density(x$age)
plot(density_of_age,main = "Density plot of age")
# creating  a Histogram of X inputs
hist(x$age,freq = FALSE,main = "Histogram and density plot of payment",xlab = "age")
lines(density_of_age, lwd = 2, col = "black")
rug(jitter(x$age))
```


```{r}
# Convert payment method to numerical values with labels
customer_shopping_data$category <- as.numeric(factor(customer_shopping_data$category, levels = unique(customer_shopping_data$category)))
# Display numerical values and their corresponding labels
method_labels <- levels(factor(customer_shopping_data$category))
method_values <- unique(unique_category)
unique_category_mapping <- data.frame(Numerical_Value = method_labels, category = method_values)
print(unique_category_mapping)
```
```{r}
# density of category
density_of_category = density(x$category)
plot(density_of_category,main = "Density plot of category")
# creating  a Histogram of X inputs
hist(x$category,freq = FALSE,main = "Histogram and density plot of category",xlab = "category")
lines(density_of_category, lwd = 2, col = "black")
rug(jitter(x$category))
```
```{r}
# convert character into numeric
x$quantity <- as.numeric(x$quantity)
# density of quantity
density_of_quantity = density(x$quantity)
plot(density_of_quantity,main = "Density plot of quantity")
# creating  a Histogram of X inputs
hist(x$quantity,freq = FALSE,main = "Histogram and density plot of quantity",xlab = "quantity")
lines(density_of_quantity, lwd = 2, col = "black")
rug(jitter(x$quantity))
```
```{r}
# Task 1.3
# plotting age against quantity
Y <- customer_shopping_data$quantity
plot(x$age,Y,main = "Correlation between age and quantity signal",xlab = "age",ylab = "quantity")
plot(x$price,Y,main = "Correlation between price and quantity signal",xlab = "price",ylab = "quantity")
plot(x$category,Y,main = "Correlation between category and quantity signal",xlab = "category",ylab = "quantity")

plot(x$payment_method,Y,main = "Correlation between payment_method and quantity signal",xlab = "payment_method",ylab = "quantity")

```
```{r}
cor_age_quantity <-cor(x$age,x$quantity)
cat("correlation coefficient between age and quantity:",cor_age_quantity,"\n")
cor_price_quantity <-cor(x$price,x$quantity)
cat("correlation coefficient between price and quantity:",cor_price_quantity,"\n")
cor_category_quantity <-cor(x$category,x$quantity)
cat("correlation coefficient between category and quantity:",cor_category_quantity,"\n")
cor_payment_method_quantity <-cor(x$payment_method,x$quantity)
cat("correlation coefficient between payment_method and quantity:",cor_payment_method_quantity,"\n")
```

```{r}
# input value
x <-x[,0:5]
cor(x)
plot(x)
pairs.panels(x[,0:5], method = "pearson", hist.col = "#00AFBB", density = TRUE, ellipses = TRUE)
```
** Task 2**
```{r}
# Task 2
x$X1 <- x$age
x$X2 <- x$category
x$X3 <- x$price
x$X4 <- x$payment_method

x <- x[,c("X1","X2","X3","X4")]


# Convert x to matrix
#x <- as.matrix(x)
y <- as.matrix(as.numeric(customer_shopping_data$quantity))
ones <- matrix(1,length(x)/4,1)

```

```{r}
alpha <- 0 
lambda <- 1
Y1 <- cbind(ones,(x[,"X4"]),(x[,"X1"])^2,(x[,"X1"])^3,(x[,"X2"])^4,(x[,"X1"])^4)
ridge_model1 <- glmnet(Y1,y,alpha = alpha , lambda = lambda)
thetaHatModel1 = coefficients(ridge_model1)
print(thetaHatModel1)
```
```{r}
Y2 <- cbind(ones,(x[,"X4"]),x[,"X1"]^3,(x[,"X3"])^4)
ridge_model2 <- glmnet(Y2,y,alpha = alpha , lambda = lambda)
thetaHatModel2 = coefficients(ridge_model2)
print(thetaHatModel2)
```

```{r}
Y3 <- cbind(ones,(x[,"X3"])^3,(x[,"X3"])^4)
ridge_model3 <- glmnet(Y3,y,alpha = alpha , lambda = lambda)
thetaHatModel3 = coefficients(ridge_model3)
print(thetaHatModel3)
```
```{r}
Y4 <- cbind(ones,(x[,"X2"]),(x[,"X1"])^3,(x[,"X3"])^4)
ridge_model4 <- glmnet(Y4,y,alpha = alpha , lambda = lambda)
thetaHatModel4 = coefficients(ridge_model4)
print(thetaHatModel4)
```

```{r}
Y5 <- cbind(ones,(x[,"X4"]),(x[,"X1"])^2,(x[,"X1"])^3,(x[,"X3"])^4)
ridge_model5 <- glmnet(Y5,y,alpha = alpha , lambda = lambda)
thetaHatModel5 = coefficients(ridge_model5)
print(thetaHatModel5)

```
```{r}
# Task 2.2
# for model 1
Y_hat_ridge1 <- predict(ridge_model1,s = lambda,newx = Y1)
# calculate residuals
residuals_ridge <- y-Y_hat_ridge1

# calculate RSS for the ridge regresssion model
Rss_ridge <- sum(residuals_ridge^2)

# Extract coefficients for the specified lambda
coefficients_ridge <- coef(ridge_model1,s = lambda)

# map coefficients to the corresponding columns of model 1
Y_hat_m1 <- as.matrix(Y1) %*% coefficients_ridge[-1]

# calculate RSS for model1
residuals_m1 <- y-Y_hat_m1
RSS_Model_1 <- sum(residuals_m1^2)
print(RSS_Model_1)
```

```{r}
# for model 2 calculate RSS 
Y_hat_ridge2 <- predict(ridge_model2,s = lambda,newx = Y2)
# calculate residuals
residuals_ridge <- y-Y_hat_ridge2

# calculate RSS for the ridge regresssion model
Rss_ridge <- sum(residuals_ridge^2)

# Extract coefficients for the specified lambda
coefficients_ridge <- coef(ridge_model2,s = lambda)

# map coefficients to the corresponding columns of model 1
Y_hat_m2 <- as.matrix(Y2) %*% coefficients_ridge[-1]

# calculate RSS for model1
residuals_m2 <- y-Y_hat_m2
RSS_Model_2 <- sum(residuals_m2^2)
print(RSS_Model_2)
```
```{r}
# calculate RSS for model 3
Y_hat_ridge3 <- predict(ridge_model3,s = lambda,newx = Y3)
# calculate residuals
residuals_ridge <- y-Y_hat_ridge3

# calculate RSS for the ridge regresssion model
Rss_ridge <- sum(residuals_ridge^2)

# Extract coefficients for the specified lambda
coefficients_ridge <- coef(ridge_model3,s = lambda)

# map coefficients to the corresponding columns of model 3
Y_hat_m3 <- as.matrix(Y3) %*% coefficients_ridge[-1]

# calculate RSS for model3
residuals_m3 <- y-Y_hat_m3
RSS_Model_3 <- sum(residuals_m3^2)
print(RSS_Model_3)
```
```{r}
# calculate RSS for model 4
Y_hat_ridge4 <- predict(ridge_model4,s = lambda,newx = Y4)
# calculate residuals
residuals_ridge <- y-Y_hat_ridge4

# calculate RSS for the ridge regresssion model
Rss_ridge <- sum(residuals_ridge^2)

# Extract coefficients for the specified lambda
coefficients_ridge <- coef(ridge_model4,s = lambda)

# map coefficients to the corresponding columns of model 4
Y_hat_m4 <- as.matrix(Y4) %*% coefficients_ridge[-1]

# calculate RSS for model4
residuals_m4 <- y-Y_hat_m4
RSS_Model_4 <- sum(residuals_m4^2)
print(RSS_Model_4)
```
```{r}
#calculate RSS for model 5
Y_hat_ridge5 <- predict(ridge_model5,s = lambda,newx = Y5)
# calculate residuals
residuals_ridge <- y-Y_hat_ridge5

# calculate RSS for the ridge regresssion model
Rss_ridge <- sum(residuals_ridge^2)

# Extract coefficients for the specified lambda
coefficients_ridge <- coef(ridge_model5,s = lambda)

# map coefficients to the corresponding columns of model 5
Y_hat_m5 <- as.matrix(Y5) %*% coefficients_ridge[-1]

# calculate RSS for model5
residuals_m5 <- y-Y_hat_m5
RSS_Model_5 <- sum(residuals_m5^2)
print(RSS_Model_5)
```
```{r}
# task 2.3
N = length(y)
# calculating the variance of model 1
variance_model1 = RSS_Model_1/(N-1)
likelihood_Model1 = -(N/2)*(log(2*pi)) -(N/2)*(log(variance_model1)) - (1/(2*variance_model1))*RSS_Model_1

# for model 2
variance_model2 = RSS_Model_2/(N-1)
likelihood_Model2 = -(N/2)*(log(2*pi)) -(N/2)*(log(variance_model2)) - (1/(2*variance_model2))*RSS_Model_2

# for model 3
variance_model3 = RSS_Model_3/(N-1)
likelihood_Model3 = -(N/2)*(log(2*pi)) -(N/2)*(log(variance_model3)) - (1/(2*variance_model3))*RSS_Model_3

# for model 4
variance_model4 = RSS_Model_4/(N-1)
likelihood_Model4 = -(N/2)*(log(2*pi)) -(N/2)*(log(variance_model4)) - (1/(2*variance_model4))*RSS_Model_4

# for model 5
variance_model5 = RSS_Model_5/(N-1)
likelihood_Model5 = -(N/2)*(log(2*pi)) -(N/2)*(log(variance_model5)) - (1/(2*variance_model5))*RSS_Model_5


# printing variance value
model1 <- c(variance_model1)
model2 <- c(variance_model2)
model3 <- c(variance_model3)
model4 <- c(variance_model4)
model5 <- c(variance_model4)
dfvariance <- data.frame(model1,model2,model3,model4,model5)
dfvariance
```
```{r}
# printing likelihood value
model1 <- c(likelihood_Model1)
model2 <- c(likelihood_Model2)
model3 <- c(likelihood_Model3)
model4 <- c(likelihood_Model4)
model5 <- c(likelihood_Model5)
dflikelihood <- data.frame(model1,model2,model3,model4,model5)
dflikelihood
```
```{r}
# Task 2.4
# Evaluating AIC and BIC of model 1
K_model1 <- length(thetaHatModel1)
AIC_model1 = 2*K_model1 - 2*likelihood_Model1
BIC_model1 = K_model1 *log(N) -2*likelihood_Model1

# for model 1
K_model2 <- length(thetaHatModel2)
AIC_model2 = 2*K_model2 - 2*likelihood_Model2
BIC_model2 = K_model2 *log(N) -2*likelihood_Model2

# for model 3
K_model3 <- length(thetaHatModel3)
AIC_model3 = 2*K_model3 - 2*likelihood_Model3
BIC_model3 = K_model3 *log(N) -2*likelihood_Model3

# for model 4
K_model4 <- length(thetaHatModel4)
AIC_model4 = 2*K_model4 - 2*likelihood_Model4
BIC_model4 = K_model4 *log(N) -2*likelihood_Model4

# for model 5
K_model5 <- length(thetaHatModel5)
AIC_model5 = 2*K_model5 - 2*likelihood_Model5
BIC_model5 = K_model5 *log(N) -2*likelihood_Model5
```

```{r}
# printing k_model value
model1 <- c(K_model1)
model2 <- c(K_model2)
model3 <- c(K_model3)
model4 <- c(K_model4)
model5 <- c(K_model5)
dfK <- data.frame(model1,model2,model3,model4,model5)
dfK
```
```{r}
model1 <- c(AIC_model1)
model2 <- c(AIC_model2)
model3 <- c(AIC_model3)
model4 <- c(AIC_model4)
model5 <- c(AIC_model5)
dfAIC <- data.frame(model1,model2,model3,model4,model5)
dfAIC
```
```{r}
model1 <- c(BIC_model1)
model2 <- c(BIC_model2)
model3 <- c(BIC_model3)
model4 <- c(BIC_model4)
model5 <- c(BIC_model5)
dfBIC <- data.frame(model1,model2,model3,model4,model5)
dfBIC
```

```{r}
# Task 2.6
model1_error <- y -Y_hat_m1
# plotting the graph QQplot and QQ line of model 1
qqnorm(model1_error,col = "darkcyan",main = "QQ plot of model 1")
qqline(model1_error,col = "red",lwd = 1)

```
```{r}
model2_error <- y -Y_hat_m2
# plotting the graph QQplot and QQ line of model 2
qqnorm(model2_error,col = "darkcyan",main = "QQ plot of model 2")
qqline(model2_error,col = "red",lwd = 1)
```
```{r}
model3_error <- y -Y_hat_m3
# plotting the graph QQplot and QQ line of model 3
qqnorm(model3_error,col = "darkcyan",main = "QQ plot of model 3")
qqline(model3_error,col = "red",lwd = 3)
```

```{r}
model4_error <- y -Y_hat_m4
# plotting the graph QQplot and QQ line of model 4
qqnorm(model4_error,col = "darkcyan",main = "QQ plot of model 4")
qqline(model4_error,col = "red",lwd = 4)
```
```{r}
model5_error <- y -Y_hat_m5
# plotting the graph QQplot and QQ line of model 5
qqnorm(model5_error,col = "darkcyan",main = "QQ plot of model 5")
qqline(model5_error,col = "red",lwd = 5)
```

```{r}
# dividing the data into training and testing into 70% and 30%
set.seed(123)
split_X <- initial_split(data = as.data.frame(x),prop = 0.7)
split_Y <- initial_split(data = as.data.frame(y),prop = 0.7)

X_training_set <- training(split_X)
X_testing_set <- testing(split_X)
Y_training_set <- as.matrix(training(split_Y))
Y_testing_set <-as.matrix(testing(split_Y))

# create the design matrix for the selected best model
training_ones <- matrix(1,nrow = nrow(X_training_set),ncol = 1)
X_training_model <- cbind(training_ones,X_training_set[,"X2"],(X_training_set[,"X1"]^3),(X_training_set[,"X3"])^4)

# Fix the typo in the next line
theta_hat <- ginv(t(X_training_model) %*% X_training_model) %*% t(X_training_model) %*% Y_training_set

#create the matrix for the testing data using the same model equation
training_ones_test <- matrix(1,nrow = nrow(X_testing_set),ncol = 1)
X_testing_model <- cbind(training_ones_test,X_testing_set[,"X2"],(X_testing_set[,"X1"])^3,(X_testing_set[,"X3"])^4)

# calculate model predictions on the testing model
Y_testing_hat <- X_testing_model %*% theta_hat


# Evaluating 95% confidence intervals for the model predictions
z <- qnorm(0.975) # z-score for 95% confidence interval
n_len <- nrow(X_testing_model)
error <- Y_testing_set - Y_testing_hat
valid_indices <- (error != 0) # check for non-zero values

# ensure that the values inside sqrt are non-negative using abs function
C_I_1 <-ifelse(valid_indices,z*sqrt(abs(error*(1-error))/n_len),0)

C_I_2 <-ifelse(valid_indices,z*sqrt(abs(error*(1+error))/n_len),0)

# plotting
plot(Y_testing_set,col = "red",pch = 19,xlab = "Index",ylab = "Y value",main = "Model predictions and 95% confidence Intervals")
points(Y_testing_hat,col = "blue",pch = 19)

# Add error bars for 95% confidence intervals
arrows(x0 = 1:n_len,y0 = Y_testing_hat - C_I_1,y1 = Y_testing_hat +C_I_2,angle = 90,code = 3,length = 0.1,col="green")
# legend
legend("topright",legend = c("Testing Data","Model predictions","95% CI"),col = c("red","blue","green"),pch = 19,cex = 0.8)

```
```{r}
# Assuming Y3 is the response variable values predicted by model 3
Y3 <- X_testing_model %*% theta_hat
theta_bias <- 0.448299550
theta_one <- 0.038109255
theta_two <- 0.009827804
theta_four <- 0.002092558
epsilon <- RSS_Model_3 * 2  # assuming RSS_Model_3 is defined

num_iterations <- 100
accepted_values_1 <- numeric(num_iterations)
accepted_values_2 <- numeric(num_iterations)
counter <- 0 

# performing rejections ABC
for (i in 1:num_iterations) {
  range1 <- runif(1, -theta_bias, theta_bias)
  range2 <- runif(1, -theta_one, theta_one)
  
  # Constructing new_theta_hat based on the dimensions of X_testing_model
  new_theta_hat <- c(range1, range2, theta_two)  # Assuming X_testing_model has 4 columns
  
  
  new_Y_Hat <- Y3 %*% new_theta_hat
  new_RSS <- sum((Y_testing_set - new_Y_Hat) ^ 2)
  
  if (new_RSS > epsilon) {
    accepted_values_1[counter + 1] <- range1
    accepted_values_2[counter + 2] <- range2
    counter <- counter + 1
  }
}

accepted_values_1 <- accepted_values_1[1:counter]
accepted_values_2 <- accepted_values_2[1:counter]

hist(accepted_values_1, main = "Histogram of Accepted values (parameters 1)")
hist(accepted_values_2, main = "Histogram of Accepted values (parameters 2)")

plot(accepted_values_1, accepted_values_2, col = c("green", "red"), 
     main = "Joint and Marginal Posterior Distribution")
```


